---
title: "Homework 1"
author: "Charlie Bonetti"
date: "2/3/21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

## Task 1

```{r mh_distance_function}
mh_distance <- function(x,y)
  if((is.logical(x) == TRUE) && (is.logical(y) == TRUE)) {
    if((is.na(x) == TRUE) || (is.na(y) == TRUE)) {
      print(-1)
      warning("x or y cannot be NA, NaN, Inf or -Inf")
    }else if(x != y) {
      print(1)
    }else {
      print(0)
    }
  }else if((is.character(x) == TRUE) && (is.character(y) == TRUE)) {
    if(nchar(x) != nchar(y)) {
      print(-1)
      warning("x and y do not have the same number of digits or letters")
    }else {
      total <- 0
      xsplit <- strsplit(x,"")[[1]]
      ysplit <- strsplit(y,"")[[1]]
      for(i in 1:length(ysplit)) {
          if(xsplit[i] != ysplit[i]) {
            total <- total + 1
          }
      }
      print(total)
    }
  }else if ((is.numeric(x) == TRUE) && (is.numeric(y) == TRUE)) {
    if(is.infinite(x) || is.nan(x) || is.na(x) || is.infinite(y) || is.nan(y) || is.na(y)) {
      print(-1)
      warning("x or y cannot be NA, NaN, Inf or -Inf")
    }else if(nchar(as.character(x)) != nchar(as.character(y))) {
      print(-1)
      warning("x and y do not have the same number of digits or letters")
    }else if((is.integer(x) == FALSE) || (is.integer(y) == FALSE)) {
      print(-1)
      warning("x or y cannot contain decimal values")
    }
    else {
      total <- 0
      xsplit <- strsplit(as.character(x),"")[[1]]
      ysplit <- strsplit(as.character(y),"")[[1]]
      for(i in 1:length(ysplit)) {
          if(xsplit[i] != ysplit[i]) {
            total <- total + 1
          }
      }
      print(total)
    }
  }else {
    print(-1)
    warning("x and y are not both logical, numeric, or character")
}
```


## Task 2

<i>
Be sure to remove chunk option `eval=FALSE` in the below code chunks
once you create `mh_distance()`. Do not include this italicized
text in your final submission.
</i>

**Initial test cases** (return a non-negative modified Hamming distance)

```{r eval=FALSE}
mh_distance(x = "abc", y = "abc")
mh_distance(x = T, y = FALSE)
mh_distance(x = "523890", y = "752839")
mh_distance(x = 2341, y = 2350)
```

Added test cases that return a non-negative modified Hamming distance result.

```{r}
mh_distance(x = 1245, y= 4873)
mh_distance(x = "cat", y = "sat")
mh_distance(x = F, y = FALSE)
mh_distance(x = "jars", y = "cars")
```

**Initial test cases** (return values of `-1`)

```{r eval=FALSE}
mh_distance(x = 52, y = 113)
mh_distance(x = "swimming", y = "winning")
mh_distance(x = NA, y = TRUE)
mh_distance(x = 1.5, y = 2.5)
```

Added test cases that return a value of `-1`.

```{r}
mh_distance(x = "car", y = 142)
mh_distance(x = 124, y = 5321)
mh_distance(x = TRUE, y = "star")
mh_distance(x = "apple", y = "map")
```


## Task 3

Consider the pair of vectors `s` and `w` given below.

```{r}
s <- c(26, 50123, 456.12, 8, 0)
w <- c(22, 50000, 451.00, 88, 0)
```

```{r}

```


## Task 4

Brief write-up goes here...
