---
title: "Homework 1"
author: "Charlie Bonetti"
date: "2/1/21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

## Task 1

```{r mh_distance_function}
mh_distance <- function(x,y) {
  
  if((typeof(x) != typeof(y)) || (is.numeric(x) == FALSE) || (is.logical(x) == FALSE) || (is.character(x) == FALSE))  {
    print("-1")
    warning("x and y are not both logical, numeric, or character")
  }
  
  if(is.infinite(x) || is.nan(x) || is.na(x) || is.infinite(y) || is.nan(y) || is.na(y)) {
    print("-1")
    warning("x or y cannot be NA, NaN, Inf or -Inf")
  }
  
  if(typeof(x) == "logical") {
    if(x == y) {print("0")}
    else(print("1"))
  }
  
  if(typeof(x) == "character") {
    if(nchar(x) != nchar(y)) {
      print("-1")
      warning("x and y are not same number of characters")
    }
    w <- strsplit(x)
  }
}

```


## Task 2

<i>
Be sure to remove chunk option `eval=FALSE` in the below code chunks
once you create `mh_distance()`. Do not include this italicized
text in your final submission.
</i>

**Initial test cases** (return a non-negative modified Hamming distance)

```{r eval=FALSE}
mh_distance(x = "abc", y = "abc")
mh_distance(x = T, y = FALSE)
mh_distance(x = "523890", y = "752839")
mh_distance(x = 2341, y = 2350)
```

Added test cases that return a non-negative modified Hamming distance result.

```{r}
# additional test cases go here
```

**Initial test cases** (return values of `-1`)

```{r eval=FALSE}
mh_distance(x = 52, y = 113)
mh_distance(x = "swimming", y = "winning")
mh_distance(x = NA, y = TRUE)
mh_distance(x = 1.5, y = 2.5)
```

Added test cases that return a value of `-1`.

```{r}
# additional test cases go here
```


## Task 3

Consider the pair of vectors `s` and `w` given below.

```{r}
s <- c(26, 50123, 456.12, 8, 0)
w <- c(22, 50000, 451.00, 88, 0)
```

```{r}
# loop goes here
```


## Task 4

Brief write-up goes here...
